### 2021-03-06 article/paper_eng.tex
fixed title page

\begin{flushleft}
\begin{tabularx}{\textwidth}{m{4.3cm}m{4.3cm}m{4.3cm}}
Daniil Gafni & Dmitry Nekhaev & Vyacheslav Demin \\
\footnotesize{Lomonosov Moscow State University, Moscow, Russia} & \multicolumn{2}{c}{\footnotesize{National Research Center <<Kurchatov Institute>>, Moscow, Russia}} \bigstrut\\
\small{danielgafni16@gmail.com} & \small{nekhaev.d.v@yandex.ru} & \small{demin.vyacheslav@mail.ru}
\end{tabularx}
\end{flushleft}

@@

\begin{flushleft}
 \begin{tabularx}{\textwidth}{lm{10cm}}
  \textbf{Funding} & {Insert Grant Name} \\
  \textbf{Data, Materials, Code} & {\href{https://github.com/danielgafni/bachelor}{https://github.com/danielgafni/bachelor}} \\
 \end{tabularx}
\end{flushleft}

@@

\begin{table}
 \caption{anti-STDP parameters}
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Рисунок & {$\tau_{+}$, мс} & {$\tau_{-}$, мс} & {$A_{+}$} & {$A_{-}$} \\
\hline
\ref{fig:worst_competition_distribution} & 14.7 & 14.2 & -0.5 & -1.5 \\
\hline
\ref{fig:medium_bad_competition_distribution} & 5.4 & 15.1 & -1.2 & -0.6 \\
\hline
\ref{fig:medium_good_competition_distribution} & 17.6 & 24.5 & -1.9 & -1.6 \\
\hline
\ref{fig:best_competition_XY} & 17.7 & 16.5 & -0.1 & -1.6\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

During the optimization of the models, the accuracy of a large number of LCSNNs was measured with various hyperparameter configurations (Fig. \ref{fig:hyperparams}). It can be seen that configurations with high accuracy (dark lines) are localized in a certain way - \textbf{EXPLAIN THIS}

>>>>

\begin{center}
\begin{tabular}{ccc}
D. Gafni \textsuperscript{a\textasteriskcentered} & D.V. Nekhaev \textsuperscript{b} & V.A. Demin \textsuperscript{b} \\
\end{tabular}

\footnotesize{
\textsuperscript{(a)} Lomonosov Moscow State University, Moscow, Russia \linebreak
\textsuperscript{(b)} National Research Center <<Kurchatov Institute>>, Moscow, Russia \linebreak
\textsuperscript{(\textasteriskcentered)} Corresponding author. Email adress: \textit{danielgafni16@gmail.com}
}

\end{center}

@@

\begin{flushleft}
 \begin{tabularx}{\textwidth}{lm{10cm}}
  \textbf{Funding} & {This work was partially supported by the Russian Science Foundation (project № 20-79-10185) in the studying of inhibitory connections training and by the grant INSERT NAME in the part of comparison of convolгtional and locally connected achitectures.} \\
  \textbf{Data, Materials, Code} & {\href{https://github.com/danielgafni/bachelor}{https://github.com/danielgafni/bachelor}} \\
  \textbf{Conflicts of Interest} & {The authors declare no conflict of interest.} \\
 \end{tabularx}
\end{flushleft}

@@

\begin{table}
 \caption{anti-STDP parameters}
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Figure & {$\tau_{+}$, ms} & {$\tau_{-}$, ms} & {$A_{+}$} & {$A_{-}$} \\
\hline
\ref{fig:worst_competition_distribution} & 14.7 & 14.2 & -0.5 & -1.5 \\
\hline
\ref{fig:medium_bad_competition_distribution} & 5.4 & 15.1 & -1.2 & -0.6 \\
\hline
\ref{fig:medium_good_competition_distribution} & 17.6 & 24.5 & -1.9 & -1.6 \\
\hline
\ref{fig:best_competition_XY} & 17.7 & 16.5 & -0.1 & -1.6\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

During the optimization of the models, the accuracy of a large number of LCSNNs was measured with various hyperparameter configurations (Fig. \ref{fig:hyperparams}). It can be seen that configurations with high accuracy (dark lines) are localized in a manner that encourages negative weight accumulation for larger time differencies $t_{post} - t_{pre}$ between -post and -pre spikes (for the anti-STDP weight update rule).
